Cycle Route Uptake and Scenario Estimation (CRUSE): an approach for developing strategic cycle network planning tools

### 2024-06-23 paper.qmd
Update for submission requirements

knitr:
  opts_chunk:
    fig.path: images/

@@

::: {#fig-dublin}
<!-- ![](images/paste-1.png) -->

![](images/paste-8.png) <!-- ![](images/paste-3.png) -->
![](images/paste-9.png)

@@

<!-- ![](images/paste-5.png) -->

<!-- ![](images/paste-6.png) -->

@@

::: {#fig-landing}
![](images/paste-10.png)

![](images/paste-11.png)

@@

# }
# ")
# schematic
# htmlwidgets::saveWidget(schematic, "images/fig5.html")
# browseURL("images/fig5.html")
# webshot2::webshot(url = "images/fig5.html", file = "images/fig5.png")
knitr::include_graphics("images/fig5.png")
```

```{=html}
<!-- ::: {#fig-user-stories}
![](images/fig5.png)

@@

```{r}
#| eval: false
#| echo: false
# Results for one city are shown below
# cities = c("dublin", "cork", "limerick", "galway")
library(tmap)
cities = c("dublin", "cork", "limerick")
city_name = "limerick"
city_buffer = zonebuilder::zb_zone(city_name)
city_buffer_5km = city_buffer |>
  filter(circle_id <= 2)
# qtm(city_buffer_5km)
city_buffer_union = sf::st_union(city_buffer_5km)
rnet_fastest = sf::read_sf(glue::glue("./../testout/{city_name}/rnet_combined_fastest.gpkg"))
rnet_fastest_city = sf::st_intersection(rnet_fastest, city_buffer_union)#
# nrow(rnet_fastest_city)
# table(rnet_fastest_city$`Bicycle (Go Dutch)`)
rnet_fastest_city_top = rnet_fastest_city |>
  filter(`Bicycle (Go Dutch)` != "1-10") |>
  filter(`Bicycle (Go Dutch)` != "0") |>
  mutate(across(`Bicycle (Baseline)`:`Quietness`, as.numeric)) |>
  slice_max(`Bicycle (Go Dutch)`, n = 10000)
m = tm_shape(rnet_fastest_city_top) +
  tm_lines(col = "Quietness", palette = "RdYlGn", lwd = 5)
tmap_save(m, "./images/rnet_fastest_city_top.png", width = 10, height = 10)
# Generalisation to balanced and quiestest route types:
route_types = c("fastest", "quietest")
dublin_rnets = purrr::map(route_types, function(route_type) {
  rnet = sf::read_sf(glue::glue("./../testout/{city_name}/rnet_combined_{route_type}.gpkg"))
  rnet_city = sf::st_intersection(rnet, city_buffer_union)
  rnet_city_top = rnet_city |>
    filter(`Bicycle (Go Dutch)` != "1-10") |>
    filter(`Bicycle (Go Dutch)` != "0") |>
    mutate(across(`Bicycle (Baseline)`:`Quietness`, as.numeric)) |>
    slice_max(`Bicycle (Go Dutch)`, n = 1000) |>
    mutate(`Route type` = route_type) |>
    rename(geometry = geom)
  rnet_city_top
})
dublin_rnets = do.call(rbind, dublin_rnets)
dublin_rnets$`Route type` = factor(dublin_rnets$`Route type`, levels = route_types)
m_types_dublin = tm_shape(dublin_rnets) +
  tm_lines(col = "col", lwd = "Bicycle (Go Dutch)", scale = 9) +
  tm_legend_hide() +
  tm_facets(by = "Route type", nrow = 1)

cities_rnet_types = purrr::map(cities, function(city_name) {
  city_buffer = zonebuilder::zb_zone(city_name)
  city_buffer_5km = city_buffer |>
    filter(circle_id <= 2)
  city_buffer_5km = stplanr::geo_bb(city_buffer_5km)
  city_buffer_union = sf::st_union(city_buffer_5km)
  route_types = c("fastest", "quietest")
  rnet_types = purrr::map(route_types, function(route_type) {
    rnet = sf::read_sf(glue::glue("./../testout/{city_name}/rnet_combined_{route_type}.gpkg"))
    rnet_city = sf::st_intersection(rnet, city_buffer_union)
    rnet_city_top = rnet_city |>
      filter(`Bicycle (Go Dutch)` != "1-10") |>
      filter(`Bicycle (Go Dutch)` != "0") |>
      mutate(across(`Bicycle (Baseline)`:`Quietness`, as.numeric)) |>
      # slice_max(`Bicycle (Go Dutch)`, n = 1000) |>
      # Title Case city name:
      mutate(`Route type` = str_to_title(route_type), `City` = str_to_title(city_name))
    rnet_city_top
  })
  rnet_types = do.call(rbind, rnet_types)
  rnet_types$`Route type` = factor(rnet_types$`Route type`, levels = str_to_title(route_types))
  rnet_types$`City` = factor(rnet_types$`City`, levels = str_to_title(cities))
  rnet_types
})
cities_rnet_types = do.call(rbind, cities_rnet_types)
# cities_rnet_types_1km = do.call(rbind, cities_rnet_types_1km)
summary(cities_rnet_types$`Bicycle (Go Dutch)`)
# Set max to 1000:
cities_rnet_types$`Bicycle (Go Dutch)` = pmin(cities_rnet_types$`Bicycle (Go Dutch)`, 1000)
m_types = tm_shape(cities_rnet_types) +
  tm_lines(col = "col", lwd = "Bicycle (Go Dutch)", scale = 20) +
  tm_legend_hide() +
  tm_facets_grid(rows = "City", columns = "Route type")
m_types
tmap_save(m_types, "./images/rnet_types.png", width = 12, height = 16)
browseURL("./images/rnet_types.png")
```

::: {#fig-city-results}
![](images/rnet_types.png)

>>>>

@@

::: {#fig-dublin}

![](paste-8.png)
![](paste-9.png)

@@

<!-- ![](paste-5.png) -->

<!-- ![](paste-6.png) -->

@@

::: {#fig-landing}
![](paste-10.png)

![](paste-11.png)

@@

# }
# ")
# schematic
# htmlwidgets::saveWidget(schematic, "fig5.html")
# browseURL("fig5.html")
# webshot2::webshot(url = "fig5.html", file = "fig5.png")
knitr::include_graphics("fig5.png")
```

```{=html}
<!-- ::: {#fig-user-stories}
![](fig5.png)

@@

```{r}
#| eval: false
#| echo: false
# Results for one city are shown below
# cities = c("dublin", "cork", "limerick", "galway")
library(tmap)
cities = c("dublin", "cork", "limerick")
city_name = "limerick"
city_buffer = zonebuilder::zb_zone(city_name)
city_buffer_5km = city_buffer |>
  filter(circle_id <= 2)
# qtm(city_buffer_5km)
city_buffer_union = sf::st_union(city_buffer_5km)
rnet_fastest = sf::read_sf(glue::glue("./../testout/{city_name}/rnet_combined_fastest.gpkg"))
rnet_fastest_city = sf::st_intersection(rnet_fastest, city_buffer_union)#
# nrow(rnet_fastest_city)
# table(rnet_fastest_city$`Bicycle (Go Dutch)`)
rnet_fastest_city_top = rnet_fastest_city |>
  filter(`Bicycle (Go Dutch)` != "1-10") |>
  filter(`Bicycle (Go Dutch)` != "0") |>
  mutate(across(`Bicycle (Baseline)`:`Quietness`, as.numeric)) |>
  slice_max(`Bicycle (Go Dutch)`, n = 10000)
m = tm_shape(rnet_fastest_city_top) +
  tm_lines(col = "Quietness", palette = "RdYlGn", lwd = 5)
tmap_save(m, "./rnet_fastest_city_top.png", width = 10, height = 10)
# Generalisation to balanced and quiestest route types:
route_types = c("fastest", "quietest")
dublin_rnets = purrr::map(route_types, function(route_type) {
  rnet = sf::read_sf(glue::glue("./../testout/{city_name}/rnet_combined_{route_type}.gpkg"))
  rnet_city = sf::st_intersection(rnet, city_buffer_union)
  rnet_city_top = rnet_city |>
    filter(`Bicycle (Go Dutch)` != "1-10") |>
    filter(`Bicycle (Go Dutch)` != "0") |>
    mutate(across(`Bicycle (Baseline)`:`Quietness`, as.numeric)) |>
    slice_max(`Bicycle (Go Dutch)`, n = 1000) |>
    mutate(`Route type` = route_type) |>
    rename(geometry = geom)
  rnet_city_top
})
dublin_rnets = do.call(rbind, dublin_rnets)
dublin_rnets$`Route type` = factor(dublin_rnets$`Route type`, levels = route_types)
m_types_dublin = tm_shape(dublin_rnets) +
  tm_lines(col = "col", lwd = "Bicycle (Go Dutch)", scale = 9) +
  tm_legend_hide() +
  tm_facets(by = "Route type", nrow = 1)

cities_rnet_types = purrr::map(cities, function(city_name) {
  city_buffer = zonebuilder::zb_zone(city_name)
  city_buffer_5km = city_buffer |>
    filter(circle_id <= 2)
  city_buffer_5km = stplanr::geo_bb(city_buffer_5km)
  city_buffer_union = sf::st_union(city_buffer_5km)
  route_types = c("fastest", "quietest")
  rnet_types = purrr::map(route_types, function(route_type) {
    rnet = sf::read_sf(glue::glue("./../testout/{city_name}/rnet_combined_{route_type}.gpkg"))
    rnet_city = sf::st_intersection(rnet, city_buffer_union)
    rnet_city_top = rnet_city |>
      filter(`Bicycle (Go Dutch)` != "1-10") |>
      filter(`Bicycle (Go Dutch)` != "0") |>
      mutate(across(`Bicycle (Baseline)`:`Quietness`, as.numeric)) |>
      # slice_max(`Bicycle (Go Dutch)`, n = 1000) |>
      # Title Case city name:
      mutate(`Route type` = str_to_title(route_type), `City` = str_to_title(city_name))
    rnet_city_top
  })
  rnet_types = do.call(rbind, rnet_types)
  rnet_types$`Route type` = factor(rnet_types$`Route type`, levels = str_to_title(route_types))
  rnet_types$`City` = factor(rnet_types$`City`, levels = str_to_title(cities))
  rnet_types
})
cities_rnet_types = do.call(rbind, cities_rnet_types)
# cities_rnet_types_1km = do.call(rbind, cities_rnet_types_1km)
summary(cities_rnet_types$`Bicycle (Go Dutch)`)
# Set max to 1000:
cities_rnet_types$`Bicycle (Go Dutch)` = pmin(cities_rnet_types$`Bicycle (Go Dutch)`, 1000)
m_types = tm_shape(cities_rnet_types) +
  tm_lines(col = "col", lwd = "Bicycle (Go Dutch)", scale = 20) +
  tm_legend_hide() +
  tm_facets_grid(rows = "City", columns = "Route type")
m_types
tmap_save(m_types, "./rnet_types.png", width = 12, height = 16)
browseURL("./rnet_types.png")
```

::: {#fig-city-results}
![](rnet_types.png)
